Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-22 paper/ms.tex
add plot_external_parameters_vs_time

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		Timeseries of ``external parameters'' for a representative
			star over one sector.
			{\it Top}: Instrumental raw magnitude (with a particular
		aperture size), as a function of time.  {\it Second and third from
			top}: $x$ and $y$ centroid positions as a function of time.
		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
		parameters, and the measured background value.
		Most of the apparent variability is instrumental.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Timeseries of ``external parameters'' for a representative star
    over one sector.  {\it Top}: Instrumental raw magnitude (with a
    particular aperture size), as a function of time.  {\it Second and
    third from top}: $x$ and $y$ centroid positions as a function of
    time.  Continuing in order are the $(s,d,k)$ PSF shape parameters,
    the CCD temperature,  and the measured background value.  Most of
    the apparent variability is instrumental.  Momentum dumps are
    marked with vertical dashed lines.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}
